---
title: "Student Sit In"
author: "Demian Romero"
date: "10/26/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this and experiment or observational study?  !-->

Data from this observational study came from 173 students from UC Davis. 



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame are seat and major.

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !-->

Both variables in this analysis are categorical; hence we use bar graphs and tables to summarize the data, and a chi-squared test for inference. 


## Data summary

**Graphical summary**

```{r}
barchartGC(~seat+major, data=UCDdataframe, main='Seat preference vs. Major')
```

The bar graph shows most students like to sit in the middle, with a higher percentage of students from Non-liberal arts majors preferring the middle.

**Numerical summary**


```{r}
tab1= xtabs(formula = ~seat+major, data=UCDdataframe,)
colPerc(tab1)
```

The numeric summary says that both liberal arts and non-liberal arts majors prefer the middle.

## Inferential Results


```{r}
chisqtestGC(tab1)
```

The p-value is 0.2173. 

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

Since the p-value is greater than .05 we fail to reject the null hypothesis and conclude we do not have the evidence to support a connect between between where one sits and one's major. This test cannot be generalized to all majors in all universities because it is not a random sample.

<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->